Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-15 scagnostics.Rmd
Rearranging table 1.

if(!file.exists("cache/indexTable.rda")){
  set.seed(505)
  res <- tableTemp()
  for(ds in c("Pipe", "Sine", "Spiral")){
    for (size in c(100, 1000)){
      for (type in c("structure", "noise")){
        res <- bind_rows(res,getIdx(ds, size, type))
      }
    }
  }
  res <- res %>% arrange(data, size, index, type) %>% select(data, size, index, type, value5, value95)
  save(res, file = "cache/indexTable.rda")
} else {
  load("cache/indexTable.rda")
}
resp <- res %>% filter(size == 1000, data == "Pipe") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
resi <- res %>% filter(size == 1000, data == "Sine") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
ress <- res %>% filter(size == 1000, data == "Spiral") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
res_all <- bind_cols(resp, resi, ress) %>%
  select(-index1, -type1, -index2, -type2) %>%
  mutate(index = fct_relevel(index, "convex", "skinny", "stringy", "dcor2D", "splines2D", "MICe", "TICe", "holes")) %>%
  arrange(index) %>%
  mutate(index = c("convex", "", "skinny", "", "stringy", "", "dcor2D", "", "splines2D", "", "MICe", "", "TICe", "", "holes", ""))
# Good resource for doing tables
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
kable(res_all, format = "latex",  caption = "Comparison of index values between noise projections and structured projections for sample size 1000, using 5th and 95th percentiles from 100 simulated sets. Most indices have much larger values for the structured projections, except for convex.", 
      col.names=c("Index","", "lower", "upper", "lower", "upper", "lower", "upper"),
      digits=2, booktabs = T) %>% 
      add_header_above(c(" ", " ", "pipe" = 2, "sine" = 2, "spiral"=2)) %>%
  group_rows("", 1, 2) %>%
  group_rows("", 3, 4) %>%
  group_rows("", 5, 6) %>%
  group_rows("", 7, 8) %>%
  group_rows("", 9, 10) %>%
  group_rows("", 11, 12) %>%
  group_rows("", 13, 14) %>%
  group_rows("", 15, 16) %>%
  kable_styling(position = "center")
```

>>>>

if(!file.exists("cache/indexTable.rda")){
  set.seed(505)
  res <- tableTemp()
  for(ds in c("Pipe", "Sine", "Spiral")){
    for (size in c(100, 1000)){
      for (type in c("structure", "noise")){
        res <- bind_rows(res,getIdx(ds, size, type))
      }
    }
  }
  res <- res %>% arrange(data, size, index, type) %>% select(data, size, index, type, value5, value95)
  save(res, file = "cache/indexTable.rda")
} else {
  load("cache/indexTable.rda")
}
resp <- res %>% filter(size == 1000, data == "Pipe") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
resi <- res %>% filter(size == 1000, data == "Sine") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
ress <- res %>% filter(size == 1000, data == "Spiral") %>%
  select(index, type, value5, value95) %>%
  rename(lower=value5, upper=value95)
res_all <- bind_cols(resp, resi, ress) %>%
  select(-index1, -type1, -index2, -type2) %>%
  mutate(index = fct_relevel(index, "holes", "convex", "skinny", "stringy", "dcor2D", "splines2D", "MICe", "TICe")) %>%
  arrange(index) %>%
  mutate(index = c("holes", "", "convex", "", "skinny", "", "stringy", "", "dcor2D", "", "splines2D", "", "MICe", "", "TICe", ""))
# Good resource for doing tables
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
kable(res_all, format = "latex",  caption = "Comparison of index values between noise projections and structured projections for sample size 1000, using 5th and 95th percentiles from 100 simulated sets. Most indices have much larger values for the structured projections, except for convex.", 
      col.names=c("Index","", "lower", "upper", "lower", "upper", "lower", "upper"),
      digits=2, booktabs = T) %>% 
      add_header_above(c(" ", " ", "pipe" = 2, "sine" = 2, "spiral"=2)) %>%
  group_rows("", 1, 2) %>%
  group_rows("", 3, 4) %>%
  group_rows("", 5, 6) %>%
  group_rows("", 7, 8) %>%
  group_rows("", 9, 10) %>%
  group_rows("", 11, 12) %>%
  group_rows("", 13, 14) %>%
  group_rows("", 15, 16) %>%
  kable_styling(position = "center")
```
